Collisions are the primary mean that the species in a plasma exchange their mass, momentum, and energy. The collisions described in this section are assumed to be entirely binary; i.e.\ involving two particles at a
time. Primarily there are two interactions that can follow a collision, namely reaction and relaxation. Reactions convert a neutral particles into ions or vice versa, which changes the composition of the plasma.
Relaxations are the main process in which a system is driven towards equilibrium in absence of external sources, is achieved by the two particles involved in a collision exchanging their velocities and temperatures
at a rate proportional the respective difference, similar to two working fluids in a heat exchanger.

\subsection{Reactions}
\label{sect:reactions}
When a free electron with a sufficient kinetic energy collides with a bound electron, the latter can receive enough energy to be removed from its orbit. This process, known as collisional ionization, requires the
free electron to have a kinetic energy $\mathcal{E}_e$ that exceeds the binding energy $\mathcal{E}_b$. Electrons in a control volume is modeled as having a single particle-averaged energy. In this section, this
averaged energy is denoted $\frac{3}{2} k_B T_e$ in this section as opposed to $\mathcal{E}_e$, which instead represents the energy of an individual electron. Collisional ionization still occurs in a volume where
$\frac{3}{2} k_B T_e < \mathcal{E}_b$ since there exists a fraction of electron with a sufficient $\mathcal{E}_e$.

Assuming a Maxwellian distribution of velocity, the probability density function (PDF) of electron speed $f(u_e)$ is \cite{Fitzpatrick}
\begin{equation}
    f(u_e) = \left( \frac{m_e}{2\pi k_B T_e} \right)^{3/2} 4\pi u_e^2 \exp{\frac{-\frac{1}{2}m_e u_e^2}{k_B T_e}}.
    \label{eqn:maxwellian_velocity}
\end{equation}

To convert Equation \ref{eqn:maxwellian_velocity} into a PDF in kinetic energy, the following identity is employed
\begin{equation}
    f(\mathcal{E}_e) \left\lvert d\mathcal{E}_e \right\rvert = f(u_e) \left\lvert du_e \right\rvert.
\end{equation}
which requires the derivative
\begin{subequations}
    \begin{align}
        \frac{d\mathcal{E}_e}{du_e} &= m_e u_e \\
        \frac{du_e}{d\mathcal{E}_e} &= \frac{1}{m_e u_e} = \frac{1}{\sqrt{2m_e \mathcal{E}_e}}
    \end{align}
\end{subequations}

The energy-PDF is therefore
\begin{subequations}
    \begin{align}
        f(\mathcal{E}_e) &= f(u_e) \left\lvert \frac{du_e}{d\mathcal{E}_e} \right\rvert \\
        &= \frac{2}{\sqrt{\pi}} \sqrt{\frac{\mathcal{E}_e}{(k_B T_e)^3}} \exp{\frac{-\mathcal{E}_e}{k_B T_e}}
    \end{align}
\end{subequations}

Let $f_b$ be the fraction of electrons with $\mathcal{E}_e \geq \mathcal{E}_b$, then
\begin{subequations}
    \begin{align}
        f_b &\equiv f(\mathcal{E}_e \geq \mathcal{E}_b) \\
        &= \int_{\mathcal{E}_b}^{\infty} f(\mathcal{E}_e) d\mathcal{E}_e \\
        &= \erfc \sqrt{z_b} + \frac{2}{\sqrt{\pi}} \sqrt{z_b} \exp(-z_b),
    \end{align}
    \label{eqn:fraction_fb}
\end{subequations}
where $z_b \equiv \mathcal{E}_b/(k_B T_e)$.

\todo{Finish up collisional ionization}

The reverse process of ionization is recombination, where an ion captures a free electron to become neutral. Recombination, fortunately, does not have an energy threshold, and the reaction rate density is
\begin{equation}
    \Gamma_{\text{rec}} = -S_{\text{rec}} n_e n_i.
\end{equation}
This reaction rate density is negative as ions are being consumed.

Reactions do not just alter the amount of each species in a plasma; it also transfer a portion of the reactant's momentum and energy directly into the product, assuming no enthalpy of reaction. These transfers
are typically more important for ions and neutrals than they are for electrons, as the latter have other sources that contribute to their momentum and energy a lot more significantly. Only account for the transfer
of conservative variables in reactive processes, the conservation equations read
\begin{subequations}
    \begin{align}
        \frac{\partial n_i}{\partial t} &= -\frac{\partial n}{\partial t} = \sum_r \Gamma_r \\
        \frac{\partial n_i \mathbf{u}_i}{\partial t} &= -\frac{\partial n \mathbf{u}}{\partial t} = \sum_r \Gamma_r \mathbf{u}_r \\
        \frac{\partial n_i \mathcal{E}_i}{\partial t} &= -\frac{\partial n \mathcal{E}}{\partial t} = \sum_r \Gamma_r \mathcal{E}_r,
    \end{align}
\end{subequations}
where the subscript $r$ both denotes the type of reaction and indicates that the variables belong to the reactant species.

\subsection{Relaxations}
\label{sect:relaxations}
A collision between a charged particle $j$ and a neutral particle results in a force roughly equal to
\begin{equation}
    \mathbf{f}_{jn} = \frac{m_j n_j (\mathbf{u}_j - \mathbf{u})}{\tau_{jn}}.
    \label{eqn:momentum_relaxation_jn}
\end{equation}
Here the double subscript $jn$ refers to a transfer from a particle $j$ to a neutral particle. By Newton's third law of motion, $\mathbf{f}_{jn} = -\mathbf{f}_{nj}$. The mean time between collisions $\tau_{jn}$
is approximately constant and is the reciprocal of the momentum-transfer collision frequency
\begin{equation}
    \nu_{jn}^M \equiv \frac{1}{\tau_{jn}} = n \sigma^{M}_{jn} \lVert \mathbf{u}_j - \mathbf{u} \rVert,
    \label{eqn:nu_jn_momentum}
\end{equation}
with $\sigma^{M}_{jn}$ denotes the equivalent cross section of momentum transfer between $j$ and $n$. It is typically a function of charged particle speed; the average value over all velocities in a Maxwellian
distribution is typically used in Equation \ref{eqn:nu_jn_momentum}.

Collisions between two charged particles are Coulomb collisions mediated by the electric field. Like-particle (electron-electron or ion-ion) collisions are often neglected because they preserve the momentum and
energy between themselves, and they contribute very little to diffusion. This is in contrast with electron-ion collisions, where there exists a net transfer of momentum (and energy) between the two particles. In a
similar formulation as Equation \ref{eqn:momentum_relaxation_jn}, the force exerted between an ion and an electron during their collision is
\begin{equation}
    \mathbf{f}_{ei} = m_e n_e (\mathbf{u}_i - \mathbf{u}_e) \nu^M_{ei},
    \label{eqn:momentum_relaxation_jn}
\end{equation}
and the electron-ion momentum-transfer collision frequency $\nu^M_{ei}$ is
\begin{equation}
    \nu^M_{ei} = C \frac{n_i Z e^4}{(4\pi\varepsilon_0)^2 \sqrt{m_e (k_B T_e)^3}} \ln\Lambda,
    \label{eqn:nu_ei_momentum}
\end{equation}
where $C$ is a prefactor on the order of $\mathcal{O}(1)$ that differs depending on the text. Chen gives $C = \pi$, while the FLASH code uses $C = \frac{4}{3} \sqrt{2\pi}$ \cite{Chen}\cite{FLASH}. $C = \pi$ will be
used in this model. The Coulomb logarithm $\ln\Lambda$ is a correction factor that accounts for the cumulative effect of many small-angle deflections in a collision and is given by
\begin{equation}
    \ln\Lambda \equiv \ln \left[ \frac{4\pi (\varepsilon_0 k_B T_e)^{3/2}}{Ze^3 \sqrt{n_e}} \right].
    \label{eqn:ln_lambda}
\end{equation}
In both Equations \ref{eqn:nu_ei_momentum} and \ref{eqn:ln_lambda}, the average ionization number $Z$ can be assumed to be 1.

For all types of collisions, the energy loss due to relaxation term can be expressed as a heat source that flows from particle $j$ to $j'$
\begin{equation}
    q'''_{jj'} = -q'''_{j'j} = \frac{3}{2} n_j \nu_{jj'}^K k_B (T_j - T_{j'}).
    \label{eqn:energy_relaxation}
\end{equation}

The energy-transfer collision frequency $\nu^K$ is related to its momentum counterpart $\nu^M$ by
\begin{equation}
    \frac{\nu_{jj'}^K}{\nu_{jj'}^M} = \frac{2m_j}{m_j + m_{j'}}.
    \label{eqn:collision_frequency_ratio}
\end{equation}

The index $j$ in Equation \ref{eqn:collision_frequency_ratio} refers to the lighter particle out of the pair, so it is always the electron if it is involved in a collision, and the ion in a ion-neutral collision.
In the former case, $\nu_{ej'}^K \ll \nu_{ej'}^M$, which means energy is relaxed at a much slower rate than momentum is. Physically, upon colliding with a heavy particle, an electron is frequently scattered before
a significant portion of its kinetic energy is lost. In an ion-neutral collision, due to the near-identical mass of the two particles, energy and momentum are relaxed on the same timescale -- i.e., $\nu_{in}^K = \nu_{in}^M$.