A plasma in itself is a collection of charges, each with its own trajectory. The most accurate plasma modelling approach is to track the position and velocity of all charged particles within the simulation domain;
however, the expense associated with such a model would be prohibitive. A fluid model approximates individual particles of like charges as a single collective body, as well as neutral particles, with each species
being described by a set of fluid equations. As a result, the electrons, ions, and neutral particles form three interpenetrating fluids. The fluids of charged particles are distinct from the neutral thanks to their
interactions with the electromagnetic fields, as described in Section \ref{sect:plasma_em}.

For the rest of this paper, the conservative and primitive variables carry the subscript $e$ for electrons and $i$ for ions. Neutral particles typically do not have a subscript; unless a particular term describes
the interaction between a neutral and a charged particle (see Section \ref{sect:plasma_collision}), then it has a subscript $n$. The subscript $j$ is a placeholder for either $e$, $i$, sometimes $n$, and $\gamma$
for photons (see Section \ref{sect:plasma_laser}).

\subsection{Conservation equations}
The neutral fluid is described as a compressible, viscous flow. Its conserved variables are described by the Navier-Stokes equations. Without external sources, these equations read
\begin{subequations}
    \begin{align}
        \frac{\partial \rho}{\partial t} + \nabla \cdot \rho \mathbf{u} &= 0 \\
        \frac{\partial \rho\mathbf{u}}{\partial t} + \nabla \cdot \rho \mathbf{u} \otimes \mathbf{u} &= -\nabla p + \nabla \cdot \mathbf{T} + \rho\mathbf{g} \\
        \frac{\partial \rho E}{\partial t} + \nabla \cdot \rho\mathbf{u} H &= -\nabla \cdot \mathbf{q}'' + \nabla \cdot \left[\mathbf{T} \cdot \mathbf{u} \right]
    \end{align}
\end{subequations}

The diffusive terms in the momentum and energy equations are $\nabla \cdot \mathbf{T}$ and $\nabla \cdot \mathbf{q}''$, respectively. The deviatoric stress tensor $\mathbf{T}$ is
\begin{equation}
    \mathbf{T} = \mu \left[ \nabla\mathbf{u} + \nabla\mathbf{u}^T - \frac{2}{3} (\nabla\cdot\mathbf{u})\mathbf{I} \right],
\end{equation}
and the heat flux vector $\mathbf{q}''$ is
\begin{equation}
    \mathbf{q}'' = -k\nabla T.
\end{equation}

Properties related to charged particles tend to be formulated in terms of their number density, so it will served the conserved variable instead of mass density. The conversion between the two densities are
\begin{equation}
    \rho_j = \frac{M_j}{N_A} n_j.
\end{equation}

Euler's equations are used to describe the flow of charged particles; viscous effects are neglected since charged particles are so accelerated by the electric fields that advection dominates over diffusion. The
Euler's equations for charged particle without external sources read
\begin{subequations}
    \begin{align}
        \frac{\partial n_j}{\partial t} + \nabla \cdot n_j \mathbf{u}_j &= 0 \\
        \frac{\partial n_j\mathbf{u}_j}{\partial t} + \nabla \cdot n_j \mathbf{u}_j \otimes \mathbf{u}_j &= \frac{-\nabla p_j}{m_j} \\
        \frac{\partial n_j \mathcal{E}_j}{\partial t} + \nabla \cdot n_j \mathbf{u}_j \mathcal{H}_j &= 0
    \end{align}
\end{subequations}
Here, the average energy and enthalpy per particle, $\mathcal{E}$ and $\mathcal{H}$, are used in order to ensure energy density is in the correct units.

\subsection{Closure relations}
For each set of conservation equations, a closer relation is required to close the system. It usually takes form of an equation of state and relates a conserved variable to a set of primitive variables.
For neutral particle, the required equations are that of density and energy as functions of pressure and temperature.
\begin{subequations}
    \begin{align}
        \rho &= \rho(p, T) \\
        \rho E &= \rho(p, T) H(p, T) - p
    \end{align}
\end{subequations}

For charged particles following a Maxwellian distribution of velocities, the average energy per particle is related to its temperature by the simple relation
\begin{equation}
    \mathcal{E}_j = \frac{3}{2} k_B T_j.
\end{equation}

Pressure is related to number density by
\begin{subequations}
    \begin{equation}
        \frac{\nabla p_j}{p_j} = \gamma \frac{\nabla n_j}{n_j},
    \end{equation}
    or
    \begin{equation}
        p_j = C_j n_j^\gamma,
    \end{equation}
\end{subequations}
where the constant $C_j$ is given by a thermodynamic equation of state.