While the model assumes the droplet is at least partially ionized, the plasma state is not formed without a laser source. The laser introduces a fourth particle -- the photon -- into the system, and it is quickly
absorbed by either bound or free electrons. Whereas the term ``electrons'' has typically referred to free electrons for much of this chapter, in this context it collectively refers to both free and bound electrons.

\subsection{Energy deposition}
This model assumes the laser beam is a line heat source within each droplet even if the laser cross-sectional area is known. The volumetric heat generation, as a result, contains a Dirac delta function
$\delta(\bm{r}_{\text{laser}})$ where $\bm{r}_{\text{laser}}$ is the laser trajectory. Finite-volume methods blend well with this assumption since the delta function is always integrated out during the formulation.
\begin{equation}
    \iiint_{\Gamma \supset \bm{r}_0 } \delta(\bm{r}_0) dV = 1
\end{equation}

Therefore, the total energy deposited in a cell that the laser passes through is the difference in laser energy at the cell entrance and exit. If the entrance energy upon cell $k$ is $I_k A$, it will have been
attenuated by a factor of $e^{-\alpha_k s_k}$ when exitting the cell -- $s_k$ being the distance that the laser beam travels within cell $k$. Therefore,

\begin{equation}
    \iiint_{V_k} q'''_{\text{laser}} dV = I_k A (1 - e^{-\alpha_k s_k})
\end{equation}

Bound and free electrons differ in how the energy is spent. A free electron, upon absorbing a photon, simply increases in kinetic energy. A bound electron, however, can either be excited or removed from its orbit altogether.
If excitation occurs, collisions with the atom causes the electron to rapidly relax and transfer the acquired energy into thermal energy of the bulk liquid; therefore, on the timescale of interest, it is responsible
to assume that the energy goes directly into heating the neutral fluid.

With two channels in which laser energy can be deposited, the total attenuation coefficient $\alpha$ is the sum of the bound and free counterparts.
\begin{equation}
    \alpha = \alpha_b + \alpha_{\text{ib}},
    \label{eqn:total_attenuation_coeff}
\end{equation}
and the fraction of energy that goes into each channel is proportional to the relative magnitude of the two absorption coefficients
\begin{subequations}
    \begin{align}
        q_b &= I_0 A(1 - e^{-\alpha s}) \frac{\alpha_b}{\alpha} \label{eqn:heat_bound_electrons} \\
        q_{\gamma e} &= I_0 A(1 - e^{-\alpha s}) \frac{\alpha_{\text{ib}}}{\alpha}.
    \end{align}
\end{subequations}

The subscript ``ib'' in Equation \ref{eqn:total_attenuation_coeff} refers to inverse bremsstrahlung, a process in which free electrons, in the vincinty of an ion, absorbs energy and starts to accelerate. The double
subscript $\gamma e$ infers as if the heat source were due to a ``collision'' between a photon and a free electron, similar to how other heat sources are denoted in Section \ref{sect:relaxations}. Inverse bremsstrahlung
should take over as the dominant absorption process once a sufficiently opaque medium is formed. The attenuation coefficient will increase proportionally to the inverse bremsstrahlung frequency $\nu_{\text{ib}}$
\begin{equation}
    \alpha_{\text{ib}} = \frac{\nu_{\text{ib}} \eta}{c} = \frac{\omega_e^2}{\omega^2 + \nu_{ei}^2} \frac{\nu_{ei} \eta}{c},
    \label{eqn:nu_ib_general}
\end{equation}
where $\omega_e$ is the plasma electron frequency and $\omega$ is the laser frequency. The former is defined as
\begin{equation}
    \omega_e^2 \equiv \frac{n_e e^2}{\varepsilon_0 m_e}.
\end{equation}

When $\omega \gg \nu_{ei}$, $\nu_{\text{ib}}$ is usually given in the form
\begin{equation}
    \nu_{\text{ib}} = \frac{n_e}{n_c} \nu_{ei},
    \label{eqn:nu_ib_approx}
\end{equation}
and the critical density $n_c$ is defined in terms of $\omega$
\begin{equation}
    \omega^2 = \frac{n_c e^2}{\varepsilon_0 m_e}.
\end{equation}

\subsection{Photoionization}
\label{sect:photoionization}
Photoionization can only occur if the photon energy, $h\nu$, exceeds the binding energy $\mathcal{E}_b$. This is simply the photoelectric effect, and it is typically caused by photons in the ultraviolet regime. For a quantum yield $\Phi \in [0, 1]$
that accounts for the number of photoelectrons produced per incident photon, the photoionization rate density is
\begin{equation}
    \Gamma_{\text{pi}} = \Phi \frac{q'''_b}{h\nu},
    \label{eqn:photoionization_rate_1}
\end{equation}
where $q'''_b$ is related to $q_b$ in Equation \ref{eqn:heat_bound_electrons} as
\begin{equation}
    \iiint q'''_b dV = q_b.
\end{equation}

A newly freed electron will carry an excess energy of $h\nu - \mathcal{E}_b$, which will be deposited towards the energy of all free electrons with a rate of
\begin{equation}
    q'''_{\text{pi}} = (h\nu - \mathcal{E}_b) \Gamma_{\text{pi}}.
    \label{eqn:electron_energy_1}
\end{equation}

Any absorption that do not result in ionization will instead excite bound electrons and serve as a heat source for the neutral particles with a rate of
\begin{equation}
    q'''_{\gamma n} = (1 - \Phi) q'''_b = q'''_b - h\nu\Gamma_{\text{pi}}.
    \label{eqn:excitation_energy_1}
\end{equation}

It is possible for a bound electron to simultaneously absorb multiple photons, a phenomenon known as multiphoton ionization \cite{Mainfray}. This instead becomes a strongly nonlinear process, and the probability of
multiple photons being absorbed by the same electron increases strongly with laser intensity. The minimum number of photons needed to completely remove an electron from its orbit is
\begin{equation}
    N \equiv \left\lceil \frac{\mathcal{E}_b}{h\nu} \right\rceil.
\end{equation}

The $N$-photon ionization rate is proportional to the $N$-th power of a particular measure of photon flux. In \cite{Mihelic}, that measure is the photon scalar flux, $\displaystyle \phi = \frac{I}{h\nu}$. However,
since the laser intensity monotonic decreases with distance travelled, it is better to calculate the ionization rate using a path-averaged scalar flux:
\begin{subequations}
    \begin{align}
        \overline{\phi} &= \frac{\overline{I}}{h\nu} \\
        &= \frac{1}{h\nu s} \int_{0}^{s} I_0 e^{-\alpha s'} ds' \\
        &= \frac{I_0}{h\nu} \frac{1 - e^{-\alpha s}}{\alpha s}
    \end{align}
\end{subequations}

The rate is then given by
\begin{equation}
    \Gamma_{\text{pi}} = \min\left( S_N \overline{\phi}^N n, \frac{q'''_b}{Nh\nu} \right)
    \label{eqn:photoionization_rate_N}
\end{equation}

Here, $S_N$ is the $N$-photon ionization rate coefficient and $n$ is the neutral particle number density. The $\min$ function is to ensure that the actual ionization rate does not exceed the photon deposition rate.
In order for $\Gamma_{\text{pi}}$ to have the correct unit, the unit of $S_N$ is m$^{2N}$ s$^{N-1}$. If Equation \ref{eqn:photoionization_rate_N} were to be in terms of another unit (for example, laser intensity)
instead, then the unit of $S_N$ must be changed accordingly. The term $N$-photon ionization cross section and the symbol $\sigma_N$ are often used in literature to describe this coefficient \cite{Mainfray}
\cite{Mihelic}; this nomenclature is not adopted here in order to ensure that all cross sections have units of area.

The rate of energy deposited into the neutrals and electrons are
\begin{subequations}
    \begin{align}
        q'''_{\text{pi}} &= (Nh\nu - \mathcal{E}_b) \Gamma_{\text{pi}} \label{eqn:electron_energy_N} \\
        q'''_{\gamma n} &= q'''_b - Nh\nu \Gamma_{\text{pi}} \label{eqn:excitation_energy_N}.
    \end{align}
\end{subequations}

For simplicity, bound electrons are assumed to only absorb $N$ photons prior to removal from its parent nucleus. Above-threshold ionization, a phenomenon where an electron absorbs more than $N$ photons, is also possible,
but will be neglected here.

% \subsection{Refraction at cell interfaces}
% \todo{Should this be in a numerical method section?}
% The refractive index $\eta$ within a droplet is a scalar field that denotes how light is continuously bent.

% The energy at which the laser exits cell $k$ is the entrance energy at cell $k'$. Assuming the index of refraction $n$ is uniform within a cell but differing from that of neighboring cells, refraction occurs at the
% cell interface according to Snell's Law.
% \begin{equation}
%     \eta_k \bm{\hat{\upomega}}_k \times \mathbf{\hat{n}}_{k,k'} = \eta_{k'}  \bm{\hat{\upomega}}_{k'} \times \mathbf{\hat{n}}_{k,k'}
% \end{equation} 

% The routine terminates once the ray exits the droplet.