The \lstinline|Box| class represents an axis-aligned rectangular prism, where its edges align with the axes in Cartesian coordinates.
It is defined by a lower vertex $\bm{p}_0$ and upper vertex $\bm{p}_1$. The edge lengths are $a = p_{x1} - p_{x0}$, $b = p_{y1} - p_{y0}$, and $c = p_{z1} - p_{z0}$,
conventially called the length, width, and height, respectively.

\subsection{Extreme points}
The extreme points are $p_{x0}$ and $p_{x1}$ in the x-direction, $p_{y0}$ and $p_{y1}$ in y, and $p_{z0}$ and $p_{z1}$ in z.

\subsection{Surface area}
The surface area is $2(ab + ac + bc)$.

\subsection{Volume}
The volume is $abc$.

\subsection{Checking if a point on the surface}
A point $\bm{r}$ is on the one of its six faces if one coordinate is equal to the minimum or maximum coordinate of the box, and the other two coordinates
are not outside of their respective extrema. For example, if $\bm{r}$ is on the face defined by $x = p_{x0}$, then $x = p_{x0}$, $p_{y0} \leq y \leq p_{y1}$, and $p_{z0} \leq z \leq p_{z1}$.

\subsection{Checking if a point is inside}
A point $\bm{r}$ is inside the box if all coordinates are strictly in between their respective extrema. Mathematically, $p_{x0} < x < p_{x1}$, $p_{y0} < y < p_{y1}$, and $p_{z0} < z < p_{z1}$.

\subsection{Checking if another volume overlaps}
\subsubsection{Box}
Two boxes overlap with for all three coordinates, the maximum value of one box is greater than the minimum value of the other.
\subsubsection{Sphere}
Refer to Section \ref{sect:collision_test_sphere}.
\subsubsection{Ellipsoid}
Refer to Section \ref{sect:collision_test_ellipsoid}.

\subsection{Distance to surface}
Given a point $\bm{r}$ on the box surface with direction $\bm{\hat{\omega}}$, it is travelling away from the box if any of the following conditions is true:
\begin{enumerate}
    \item $x = p_{x0}$ and $\Omega_x \leq 0$,
    \item $x = p_{x1}$ and $\Omega_x \geq 0$,
    \item $y = p_{y0}$ and $\Omega_y \leq 0$,
    \item $y = p_{y1}$ and $\Omega_y \geq 0$,
    \item $z = p_{z0}$ and $\Omega_z \leq 0$,
    \item $z = p_{z1}$ and $\Omega_z \geq 0$.
\end{enumerate}
The distance to surface should be 0 in these cases according to the function definition.

Otherwise, the distance $s$ to the plane (not the box face) $x = p_{x0}$ is
\begin{equation}
    s = \frac{x - p_{x0}}{\Omega_x},
\end{equation}
and similar formulae can be applied to the other planes containing a box face.

Even if negative or undefined values of $s$ are neglected, the smallest positive value of $s$ is still not guaranteed to be the distance to the box surface.
This is because the calculated $s$ is the distance to the plane containing a face, not the face itself. An additional check to ensure that after traveling a
distance $s$ to reach a plane, the remaining two coordinates are still in bound. For example, if $s$ is the distance to the plane $x = p_{x0}$, the additional
checks are
\begin{align}
    p_{y0} \leq y + \Omega_y s \leq p_{y1} \\
    p_{z0} \leq z + \Omega_z s \leq p_{z1}
\end{align}

The smallest positive value of $s$ that also ensures the point is still in bound is the distance to the box surface.

\subsection{Outward normal vector}
For a point $\bm{r}$ on the box surface, the normal vector is undefined if $\bm{r}$ lies on a vertex or an edge (the intersection of multiple faces). Otherwise,
the normal vector is only dependent on which face the point lies:
\begin{enumerate}
    \item If $x = p_{x0}$, $\bm{\hat{n}} = -\bm{\hat{\imath}}$
    \item If $x = p_{x1}$, $\bm{\hat{n}} = +\bm{\hat{\imath}}$
    \item If $y = p_{y0}$, $\bm{\hat{n}} = -\bm{\hat{\jmath}}$
    \item If $y = p_{y1}$, $\bm{\hat{n}} = +\bm{\hat{\jmath}}$
    \item If $z = p_{z0}$, $\bm{\hat{n}} = -\bm{\hat{k}}$
    \item If $z = p_{z1}$, $\bm{\hat{n}} = +\bm{\hat{k}}$
\end{enumerate}

\subsection{Checking if another volume is inside}
This function is only defined for the \lstinline|Box| class, which will be useful in a few tree functions. Given a volume with calculated extreme points $\bm{r}_0$ and $\bm{r}_1$, respectively, the box will completely
enclose this volume if the following 6 conditions are true
\begin{enumerate}
    \item $p_{x0} \leq x0$
    \item $p_{y0} \leq y0$
    \item $p_{z0} \leq z0$
    \item $p_{x1} \geq x1$
    \item $p_{y1} \geq y1$
    \item $p_{z1} \geq z1$
\end{enumerate}